Generality in food webs scales with species richness, not latitude

### 2015-04-13 manuscript/latitudepaper.tex
Updated betas

Link density, generality, and vulnerability each increased with increasing
species richness (Fig.~\ref{S}; $\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675,
$p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001 respectively).  For estuarine,
marine, and terrestrial food webs this increase did not vary with latitude
($\beta_{Latitude}$=-0.001, $p$=0.334 for link density; $\beta_{Latitude}$=-0.001, $p$=0.354 for generality;
and $\beta_{Latitude}$=-0.001, $p$=0.334 for vulnerability). In lake food webs, link density,
generality, and vulnerability all increased more quickly towards the poles
($\beta_{Latitude:Lake}$=0.004, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
$p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
stream food webs generality increased more rapidly towards the poles 
($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability did not vary with latitude.

@@

In contrast to the proportion of basal resources, link density, generality,
and vulnerability tended to increase with increasing proportions of
intermediate consumers (Fig.~\ref{I}). The best-fit models for scaling of link
density and vulnerability with the proportion of intermediate consumers did
not include any effect of latitude on scaling in any ecosystem type. Generality
increased more rapidly towards the equator in estuarine, lake, marine, and
stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
$p$=0.053). In lake and stream food webs, generality increased more slowly
with the proporiton of intermediate consumers such that, at low proportions,
the effect of latitude could negate or reverse the increase.

As with the proportion of basal resources; link density, generality, and
vulnerability decreased as the proportion of top predators increased. For
estuarine, lake, and marine food webs scaling of link density, generality, and
vulnerability did not vary significantly with latitude
($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
$\beta_{Latitude}$=-0.001, $p$=0.526 for vulnerability; the best-fit model for
generality did not include any terms for latitude in any ecosystem type). In
stream and terrestrial food webs, the decrease in link density and
vulnerability was less sharp towards the poles, although this trend was
significant only in streams ($\beta_{Latitude:Stream}$=0.015,
$p$\textless0.001 and $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link
density; $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
$\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability).

>>>>

Link density, generality, and vulnerability each increased with increasing
species richness (Fig.~\ref{S}; $\beta_0$=0.666, $p$\textless0.001; $\beta_0$=0.623,
$p$\textless0.001; and $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine,
marine, and terrestrial food webs this increase did not vary with latitude
($\beta_{Latitude}$=-0.001, $p$=0.267 for link density; $\beta_{Latitude}$=-0.001, $p$=0.363 for generality;
and $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability). In lake food webs, link density,
generality, and vulnerability all increased more quickly towards the poles
($\beta_{Latitude:Lake}$=0.005, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
$p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
stream food webs generality increased more rapidly towards the poles 
($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability did not vary with latitude.

@@

In contrast to the proportion of basal resources, link density, generality,
and vulnerability tended to increase with increasing proportions of
intermediate consumers (Fig.~\ref{I}; ). The best-fit models for scaling of link
density and vulnerability with the proportion of intermediate consumers did
not include any effect of latitude on scaling in any ecosystem type. Generality
increased more rapidly towards the equator in estuarine, lake, marine, and
stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
$p$=0.053). In lake and stream food webs, generality increased more slowly
with the proporiton of intermediate consumers such that, at low proportions,
the effect of latitude could negate or reverse the increase.

As with the proportion of basal resources; link density, generality, and
vulnerability decreased as the proportion of top predators increased. For
estuarine, lake, and marine food webs scaling of link density, generality, and
vulnerability did not vary significantly with latitude
($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
$\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the best-fit model for
generality did not include any terms for latitude in any ecosystem type). In
stream and terrestrial food webs, the decrease in link density and
vulnerability was less sharp towards the poles, although this trend was
significant only in streams ($\beta_{Latitude:Stream}$=0.015,
$p$\textless0.001 and $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link
density; $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
$\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability).
